Windowed Developer Topic Analysis

### 2009-03-27 lda-paper.tex
described firebird

%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird

XXX need results!

@@

XXX needs results

@@

The plots we produced of MaxDB 7.500 were interesting, there was a
period where no real development occured and thus there were no topics
whatsoever. We have two periods to evaluate for MaxDB 7.500, the first
period from June 2004 to jan 2005, and the second period from June
2005 to June 2006.

>>>>

%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql

@@

%XXX needs results

We tracked Firebird from August 2000 to January 2006.
Our first attempt with Firebird resulted in a set of trends that were
dominated by one large trend containing tokens which were mostly stop
words such as ``the to a for of is it'' and references to one author
\texttt{carlosga05}.

The second largest trend related to branching and possibly merging, it
contained language such as ``was added on branch'' and contained
references to tags and branches.

The third largest trend contained reference to the changelog, the
build system, architecture and platform support. It specifically
mentioned tokens such as ``Solaris port x86''.

Other trends included topics regarding AIX PPC compilation, updating
the build process, internationalization and UTF8, Darwin build support
and bug fixing.

Topics that were not trends that were interesting were external bug
fixes submitted to the project, the developers would write thank yous
in their changelog comments: ``thanks Bill Lam''. Other interesting
topics include tokens and topics such as: ``compiler workarounds'', ``nightly updates'', packets and MSVC++,

@@

The plots we produced of MaxDB 7.500 were interesting, there was a
period where no real development occured and thus there were no topics or trends
whatsoever. We have two periods to evaluate for MaxDB 7.500, the first
period from June 2004 to jan 2005, and the second period from June
2005 to June 2006.
